Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-08 paper/intro.tex
Paper update

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems. The aim is to find the optimal design parameters that provide
the best circuit performance, which can be represented by a figure of merit (FOM)
function. Prior works about analog circuit optimization include offline
model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
accurate global models and then optimize the cheap-to-evaluate models. The
problem of this approach is that the accurate models are usually hard to get.
For example, in~\cite{wang2014enabling}, 100,000 randomly simulated points are
used to train a sparse polynomial model for an amplifier circuit with ten
design parameters.

Simulation-based methods, instead, treat the performances of the circuits as black-box functions. The performances are obtained from circuit simulations. Global optimization
algorithms are then directly applied to the black-box functions. For
simulation-based circuit optimization methods, meta-heuristic
algorithms~\cite{phelps2000anaconda, liu2009analog} are widely used. Although
these algorithms can explore the whole design space, they have relatively low
convergence rate. When the circuit simulation takes a long time, both
model-based and simulation-based approaches can be very time-consuming.

% TODO: Bayesian optimization is a sequential algorithm, there is a need to
% parallelize it
%
% TODO: cite the two 3D-IC papers of TVLSI
To reduce the number of circuit simulations, the Gaussian process
(GP)~\cite{GPML} model has been introduced as an online surrogate model to
assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
differential evolution algorithm. Recently, the
Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been
applied for analog circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization algorithm is
firstly introduced for the single- and multi-objective optimization of general analog circuits and has
shown to be more efficient compared to other simulation-based
approaches. In~\cite{wang2017efficient}, the Bayesian optimization algorithm
is combined with adaptive Monte-Carlo sampling to optimize the yield of analog
circuits and static random-access memory (SRAM).

@@

% TODO: Beiefly introduce my algorithm
All the algorithms mentioned above choose to use single acquisition function,
except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition
function. The other parallelization methods rely on a specific acquisition
function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
the knowledge gradient method must be used for the qKG algorithm. As is stated
in~\cite{hoffman2011portfolio}, no single acquisition function can always
outperform other acquisition functions. Relying on one acquisition function may
result in poor performance.

>>>>

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems. The aim is to find the optimal design parameters that provide
the best circuit performance, which can be represented by a figure of merit (FOM)
scalar real-valued function. Prior works about analog circuit optimization include offline
model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
accurate global models of the FOM and then optimize the cheap-to-evaluate models. The
problem of this approach is that the accurate models are usually hard to get.
For example, in~\cite{wang2014enabling}, 100,000 randomly simulated points are
used to train a sparse polynomial model for an amplifier circuit with ten
design parameters.

Simulation-based methods, instead, treat the performances of the circuits as black-box functions. The performances are obtained from circuit simulations. Global optimization
algorithms are directly applied to the black-box functions. For
simulation-based circuit optimization methods, meta-heuristic
algorithms~\cite{phelps2000anaconda, liu2009analog} are widely used. Although
these algorithms can explore the whole design space, they have relatively low
convergence rate. When the circuit simulation takes a long time, both
model-based and simulation-based approaches can be very time-consuming.

% TODO: Bayesian optimization is a sequential algorithm, there is a need to
% parallelize it
%
% TODO: cite the two 3D-IC papers of TVLSI
To reduce the number of circuit simulations, the Gaussian process
(GP)~\cite{GPML} model has been introduced as an online surrogate model to
assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
differential evolution algorithm. Recently, the
Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been
applied for analog circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization algorithm is
firstly introduced for the single- and multi-objective optimization of general analog circuits and has
shown to be more efficient compared with other simulation-based
approaches. In~\cite{wang2017efficient}, the Bayesian optimization algorithm
is combined with adaptive Monte-Carlo sampling to optimize the yield of analog
circuits and static random-access memory (SRAM).

@@

% TODO: Beiefly introduce my algorithm
All the algorithms mentioned above choose to use single acquisition function.
And except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition
function, other parallelization methods rely on a specific acquisition
function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
the knowledge gradient (KG) acquisition function must be used for the qKG algorithm. As is stated
in~\cite{hoffman2011portfolio}, no single acquisition function can always
outperform other acquisition functions. Relying on one acquisition function may
result in poor performance.
